--- 
title: "A Minimal Book Example"
author: "Yihui Xie (Workshop material by Nils Holmberg)"
date: "`r Sys.time()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
github-repo: rstudio/bookdown-demo
description: "This is a minimal example of using the bookdown package to write a book. The output format for this example is bookdown::gitbook."
---

# Workshop 211021

## workshop material 

- in order to follow along, please download github repo as zip file [https://github.com/nils-holmberg/sfac-r/archive/refs/heads/main.zip](https://github.com/nils-holmberg/sfac-r/archive/refs/heads/main.zip)
- unzip repo file and find it in rstudio, demo will be held using [https://rstudio.cloud](https://rstudio.cloud) by uploading zip file here

## install libs

```{r, eval=F}
install.packages("rmarkdown")
install.packages("bookdown")
install.packages("rsconnect")
#install.packages("bslib")
#library(rmarkdown)
#library(bookdown)
```

## test rmarkdown

- we are going to use rmarkdown to render a single Rmd document, cd to sfac-r-main/web/bkd/workshop

```{r, eval=F}
#setwd("/cloud/project/sfac-r-main/web/bkd")
rmarkdown::render('document1.Rmd', output_format='all', output_dir='./')
#rmarkdown::render('document2.Rmd', output_format='all', output_dir='./')
```

- the output formats are specified in the yaml header of the Rmd file, you can preview the result by opening the output file

## test bookdown

- now we are going to try to render a collection of Rmd files as a book, the original bookdown demo can be found on github [https://github.com/rstudio/bookdown-demo](https://github.com/rstudio/bookdown-demo), but you can also change directory to sfac-r-main/web/bkd 

```{r, eval=F}
#setwd("/cloud/project/sfac-r-main/web/bkd")
bookdown::render_book('index.Rmd', output_dir='./')
```

- the output formats are specified in the yaml header of the index.Rmd file, you can preview the result of any changes by opening the index.html file

## publish book

- if we have a git client and a github account, the book could now be published to github 
- however, we can also choose to publish to the web service [https://bookdown.org/](https://bookdown.org/) by creating a free account there

```{r, eval=F}
# rstudio connect package
rsconnect::accounts()
```

- the following commands can also be accessed more easily through the rstudio gui
- connect your r client to .....
- when publishing the bookdown book, we need to stand in the correct working directory

```{r, eval=F}
#setwd("/cloud/project/sfac-r-main/web/bkd")
bookdown::publish_book(render="local", account="nils.holmberg", server="bookdown.org", name="sfac-r-bookdown")
```

## troubleshoot

```{r, eval=F}
rsconnect::deployments(".")
#rsconnect::forgetDeployment(dryRun = TRUE)
#rsconnect::deploySite(account="nils.holmberg", siteName="sfac-r-bookdown", appId=9002, server="bookdown.org")
```


```{r, eval=F}
```





