---
title: "Confirmatory Factor Analysis"
author: "Nils Holmberg"
date: "210401"
---
<br/>

## Read SPSS data into R
Haven enables R to read and write various data formats used by other statistical packages by wrapping the fantastic ReadStat C library written by Evan Miller. Haven is part of the tidyverse.

- https://haven.tidyverse.org/
- https://rstudio.cloud/project/2337715

```{r}
#read spss files .sav
#install.packages("haven", lib="~/lib/r-cran")
#install.packages("haven", lib="C:/Program Files/R/lib")
library(haven)

#project string
pstr = "csv/dataset-iss-2016-subset1"
pstr = "../../csv/dataset-iss-2016-subset1"

#read sav
dfs = read_sav(paste0(pstr, ".sav"))
#get labels
dfl = data.frame(label=sapply(dfs, function(x) attributes(x)$label))
dfl$vars = rownames(dfl)

#export csv
write.table(dfs, paste0(pstr, ".csv"), sep="\t", row.names=F)
#read csv
dfs = read.table(paste0(pstr, ".csv"), sep='\t', header=T, strip.white=TRUE, stringsAsFactors=FALSE)
```

## CFA using package "lavaan"
The lavaan package is developed to provide useRs, researchers and teachers a free open-source, but commercial-quality package for latent variable modeling. You can use lavaan to estimate a large variety of multivariate statistical models, including path analysis, confirmatory factor analysis, structural equation modeling and growth curve models.

- https://lavaan.ugent.be/index.html

```{r}
#install.packages("lavaan", dependencies=TRUE, lib="~/lib/r-cran")
#install.packages("lavaan", dependencies=TRUE, lib="C:/Program Files/R/lib")
library(lavaan)

#specify latent variables
animosity       =~ ANI1 + ANI2 + ANI3 + ANI4
ethnocentrism   =~ ETHNO1 + ETHNO2 + ETHNO3

#specify model
iss.cfa.model <- '
animosity       =~ ANI1 + ANI2 + ANI3 + ANI4
ethnocentrism   =~ ETHNO1 + ETHNO2 + ETHNO3
'
#fit model
fit <- cfa(iss.cfa.model, data=dfs)

#get model info
summary(fit, fit.measures=TRUE)
```

## cfa using lavaan
data contains observations of..
```{r}
#
```

## cfa using lavaan
data contains observations of..
```{r}
#
```

## cfa using lavaan
data contains observations of..
```{r}
#
```



